Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2022-10-24 paper-correlations.tex
Example of calculations

\begin{figure*}[pt]
  \centering
  \subfigure[Bandera Brown sandstone]{
    \includegraphics[width=0.3\linewidth]{real-data/BanderaBrown_2d25um_binary.png}
    \label{fig:bandera}}
  \hfill
  \subfigure[Bentheimer sandstone]{
    \includegraphics[width=0.3\linewidth]{real-data/Bentheimer_2d25um_binary.png}
    \label{fig:bentheimer}}
  \hfill
  \subfigure[Kirby sandstone]{
    \includegraphics[width=0.3\linewidth]{real-data/Kirby_2d25um_binary.png}
    \label{fig:kirby}}
  \vskip\baselineskip
  \subfigure[Sandstone 1]{
    \includegraphics[width=0.3\linewidth]{real-data/sandstone1.png}
    \label{fig:real-sandstone-1}}
  \hfill
  \subfigure[Sandstone 2]{
    \includegraphics[width=0.3\linewidth]{real-data/sandstone2.png}
    \label{fig:real-sandstone-2}}
  \hfill
  \subfigure[Carbonate 1]{
    \includegraphics[width=0.3\linewidth]{real-data/carbonate1.png}
    \label{fig:real-carbonate-1}}
  \caption[]{Plots of correlation functions for real samples.}
  \label{fig:real-data}
\end{figure*}

>>>>

\begin{figure*}[pt]
  \centering
  \subfigure[Bandera Brown sandstone]{
    \includegraphics[width=0.3\linewidth]{real-data/BanderaBrown_2d25um_binary.png}
    \label{fig:bandera}}
  \hfill
  \subfigure[Bentheimer sandstone]{
    \includegraphics[width=0.3\linewidth]{real-data/Bentheimer_2d25um_binary.png}
    \label{fig:bentheimer}}
  \hfill
  \subfigure[Kirby sandstone]{
    \includegraphics[width=0.3\linewidth]{real-data/Kirby_2d25um_binary.png}
    \label{fig:kirby}}
  \vskip\baselineskip
  \subfigure[Bandera Brown sandstone (correlation functions)]{
    \includegraphics[width=0.3\linewidth]{real-data/BanderaBrown_2d25um_binary-plot.png}
    \label{fig:bandera-plt}}
  \hfill
  \subfigure[Bentheimer sandstone (correlation functions)]{
    \includegraphics[width=0.3\linewidth]{real-data/Bentheimer_2d25um_binary-plot.png}
    \label{fig:bentheimer-plt}}
  \hfill
  \subfigure[Kirby sandstone (correlation functions)]{
    \includegraphics[width=0.3\linewidth]{real-data/Kirby_2d25um_binary-plot.png}
    \label{fig:kirby-plt}}
  \vskip\baselineskip
  \subfigure[Sandstone 1]{
    \includegraphics[width=0.3\linewidth]{real-data/sandstone1.png}
    \label{fig:real-sandstone-1}}
  \hfill
  \subfigure[Sandstone 2]{
    \includegraphics[width=0.3\linewidth]{real-data/sandstone2.png}
    \label{fig:real-sandstone-2}}
  \hfill
  \subfigure[Carbonate 1]{
    \includegraphics[width=0.3\linewidth]{real-data/carbonate1.png}
    \label{fig:real-carbonate-1-plt}}
  \vskip\baselineskip
  \subfigure[Sandstone 1 (correlation functions)]{
    \includegraphics[width=0.3\linewidth]{real-data/sandstone1-plot.png}
    \label{fig:real-sandstone-1-plt}}
  \hfill
  \subfigure[Sandstone 2 (correlation functions)]{
    \includegraphics[width=0.3\linewidth]{real-data/sandstone2-plot.png}
    \label{fig:real-sandstone-2-plt}}
  \hfill
  \subfigure[Carbonate 1 (correlation functions)]{
    \includegraphics[width=0.3\linewidth]{real-data/carbonate1-plot.png}
    \label{fig:real-carbonate-1}}
  \caption[]{Plots of correlation functions for real samples.}
  \label{fig:real-data}
\end{figure*}
